Distinguishing NFW and Isothermal Density Profiles with Weak Gravitational Lensing

### 2018-05-08 paper.tex
Finished CIS section

\subsection{Cored Isothermal Sphere Profile}
The cored isothermal sphere (CIS) profile is related to the singular isothermal sphere (SIS) profile, which is often used to describe halos and other collapsed astrophysical objects because of its simple formulation. Unlike the singular isothermal sphere, the cored isothermal sphere does not have a density singularity at its center due to a finite core radius $r_c$. The CIS density profile is defined
\begin{equation} \label{cisdensity}
\rho_\mathrm{CIS}(r) = \frac{\sigma^2}{2\pi G (r^2 + {r_c}^2)},
\end{equation}
where $\sigma^2$ is the velocity dispersion of the halo \citep{Chen2005, Shapiro1999}. Applying equation \ref{sigma} and defining $\theta_c = r_c/D_L$, we get the projected surface density of the CIS profile:
\begin{equation}
\Sigma_\mathrm{CIS}(\theta) = \frac{\sigma^2}{2 G D_L \sqrt{\theta^2 + {\theta_c}^2}}
\end{equation}
The average surface density inside angular radius $\theta$ is derived using equation \ref{sigmabar}:
\begin{equation}
\overline{\Sigma}_\mathrm{CIS}(\theta) = \frac{\sigma^2 \left(\sqrt{\theta^2 + {\theta_c}^2} - \theta_c \right)}{G D_L \theta^2}
\end{equation}
The tangential shear follows from equation \ref{tangentialshear}:
\begin{equation}
\gamma_\mathrm{CIS}(\theta) = \frac{\sigma^2 \left(\sqrt{\theta^2 + {\theta_c}^2} - \theta_c \right)}{\Sigma_\mathrm{crit} G D_L \theta^2} - \frac{\sigma^2}{2 \Sigma_\mathrm{crit} G D_L \sqrt{\theta^2 + {\theta_c}^2}}
\end{equation}
The ellipticity equations, while not quite elegant, are trivial to calculate from the shear.

@@

\subsection{Navarro-Frenk-White (NFW) Profile}

\begin{equation}
\rho_\mathrm{NFW}(r) = \frac{\rho_\mathrm{crit} \delta_c}{(r/r_s)\left(1 + r/r_s\right)^2}
\end{equation}

>>>>

\subsection{Cored Isothermal Sphere Profile}
The cored isothermal sphere (CIS) profile is related to the singular isothermal sphere (SIS) profile, which is often used to describe halos and other collapsed astrophysical objects because of its simple formulation. Unlike the singular isothermal sphere, the cored isothermal sphere does not have a density singularity at its center due to a finite core radius $r_c$. The CIS density profile is defined
\begin{equation} \label{cisdensity}
\rho_\mathrm{CIS}(r) = \frac{\sigma^2}{2\pi G (r^2 + {r_c}^2)},
\end{equation}
where $\sigma^2$ is the velocity dispersion of the halo \citep{Chen2005, Shapiro1999}. Applying equation \ref{sigma} and defining $\theta_c = r_c/D_L$, we get the projected surface density of the CIS profile:
\begin{equation}
\Sigma_\mathrm{CIS}(\theta) = \frac{\sigma^2}{2 G D_L \sqrt{\theta^2 + {\theta_c}^2}}
\end{equation}
The average surface density inside angular radius $\theta$ is derived using equation \ref{sigmabar}:
\begin{equation}
\overline{\Sigma}_\mathrm{CIS}(\theta) = \frac{\sigma^2 \left(\sqrt{\theta^2 + {\theta_c}^2} - \theta_c \right)}{G D_L \theta^2}
\end{equation}
The tangential shear follows from equation \ref{tangentialshear}:
\begin{equation}
\gamma_\mathrm{CIS}(\theta) = \frac{\sigma^2}{\Sigma_\mathrm{crit} G D_L} \left(\frac{\sqrt{\theta^2 + {\theta_c}^2} - \theta_c}{\theta^2} - \frac{1}{2 \sqrt{\theta^2 + {\theta_c}^2}}\right)
\end{equation}
The ellipticity equation, while not quite elegant, is trivial to calculate using equation \ref{ellipticity}.

@@

\subsection{Navarro-Frenk-White (NFW) Profile}
The NFW profile has had some success in describing dark matter halos is both simulations and observations, though
\citep{Navarro1997}
\begin{equation}
\rho_\mathrm{NFW}(r) = \frac{\rho_\mathrm{crit} \delta_c}{(r/r_s)\left(1 + r/r_s\right)^2}
\end{equation}
